Self-Supervised Transfer Learning From 2D Images to 3D Point Clouds

### 2022-04-04 doc/paper.tex
Completes the first draft of the methods section

@@

With the mapping, we can now

Transformations applied to 3D points.

How the loss was formulated in the 2D to 3D transfer.

What does the loss function look like?

\section{Downstream Tasks}
\label{sec:downstream}

\newpage
\section{Experiment Results}
\label{sec:results}

>>>>

\AJ{Need to review how I do this in the code, I think I use a projector left over from BYOL}

@@

Our last step, after generating 2D features and mapping them to 3D points is to train our 3D model to emulate our pre-trained features. We accomplish this using the same contrastive loss from \ref{eq:contrastive_loss} but with input embeddings $\mathbf{z}_i$ coming from the features of the 3D points and its positive and negative embeddings $\mathbf{z}_i^{+},\mathbf{z}_i^{-}$ coming from the corresponding 2D feature.

Only the required transformations are applied to the 2D image. These being: resizing, square cropping and colour normalization. Point cloud coordinates are transformed with a random horizontal flip and random rotation around the $z$ axis while their colors are transformed using autocontrast, translation and jitter.

We use the same 3D model as in \cite{xie2020pointcontrast}. For downstream tasks, the final $1\times1$ convolution is thrown away as the decoder.

\AJ{Need to look at not using a projection head in 3D model.}

\section{Experiment Results}
\label{sec:results}
